### 2014-03-20 paper/designspace.tex
addressing some comments, but mostly just copying the tovi comments in

\section{The Design Space of Pipes}
We propose the use of pipes to redirect active components through the core and onto the surface of 3D printed interactive objects, as well as to allow for the creation of designed paths.  By using different types and topologies of pipes and inserting different media into the completed pipes, a variety of inputs and outputs can be located at arbitrary points on the surface of a 3D print.  We describe the design space of pipes, and then follow up with some of the input and output possibilities---both those that have been previously explored and those that are possible but remain unexplored.

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/tubespace.pdf}
\caption{The design space of pipes.  Pipe types, media, topologies, and design are discussed more fully in the text.}
\label{fig:pipespace}
\end{figure}

@@

@@

\begin{figure*}[t]
\centering
    \includegraphics[width=\textwidth]{figures/designspace.pdf}
\caption{The design space of pipe-based interactions.  Existing systems are written in regular font.  Those created with fabrication are in {\color{blue}blue}. In \emph{{\color{red}red italic}} are unexplored interactions creatable with custom-fabricated pipes.}
\label{fig:designspace}
\end{figure*}

@@

Touch sensing is enabled through pipes filled with conductive media.  Traditional wires (threadable) may be used, but we have had success with conductive paint (liquid).  Using conductive paint and Swept Frequency Capacitive Sensing (SFCS \cite{Sato-touche}), an interior star pipe topology can enable single-wire touch- and grasp-sensing at any set of points on a printed object's surface (see Figure \cite{fig:toy}).  Simple capacitance measurements are possible using the same media, and custom-designed sensors like those created in Savage, et al.,'s Midas system are also possible \cite{Savage-midas}.

@@

\subsection{Identity}

Pipes included in printed objects allow for their identification.  While the pipes need not be visible (especially in the case of fully-enclosed pipes), their presence, location, network structure, and length change many properties of a printed object.  This includes weight, acoustic resonance, and (if conductive material is present) capacitive signature.

@@

>>>>

\section{The Design Space of Pipes}
The design space of pipes is large.  By using different types and topologies of pipes and inserting different media into the completed pipes, a variety of inputs and outputs can be located at arbitrary points on the surface of a 3D print.  We describe the  space, and then follow up with some of the input and output possibilities---both those that have been previously explored and those that are possible but remain unexplored.  We also discuss some possible implications of pipes in 3D prints.

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/tubespace.pdf}
\caption{The design space of pipes.  Pipe types, media, topologies, and design are discussed more fully in the text.}
\label{fig:pipespace}
\end{figure}

@@

\tovi{The table indicates that media is the most
prominent variable in the design space.
Should justify that.
}

\tovi{There's lots of great ideas an examples in the inputs and outputs section, but the orgnization and coorespondence to the table is a little hard to follow. }

@@

\begin{figure*}[t]
\centering
    \includegraphics[width=\textwidth]{figures/designspace.pdf}
\caption{The design space of pipe-based interactions.  Existing systems are written in regular font.  Those created with fabrication are in {\color{blue}blue}. In \emph{{\color{red}red italic}} are unexplored interactions creatable with custom-fabricated pipes. \tovi{Im not sure how well this table will work. Division between input and output should be more prominent.}}
\label{fig:designspace}
\end{figure*}

@@

Touch sensing can be enabled through pipes filled with conductive media.  Traditional wires (threadable) may be used, but conductive paint (liquid) may be more flexible.  Using conductive paint and Swept Frequency Capacitive Sensing (SFCS \cite{Sato-touche}), an interior star pipe topology can enable single-wire touch- and grasp-sensing at any set of points on a printed object's surface (see Figure \cite{fig:toy}).  Simple capacitance measurements are possible using the same media, and custom-designed sensors like those created in Savage, et al.,'s Midas system are also possible \cite{Savage-midas}.

@@

\subsection{Implications}

\tovi{Where does this fit in the design space? This seciton seems out of place.
}

\valkyrie{is this something we want to talk about at all?}

Pipes included in objects can have additional effects beyond their designed intentions.

Pipes included in printed objects allow for their identification.  While the pipes need not be visible (especially in the case of fully-enclosed pipes), their presence, location, network structure, and length change the physical properties of a printed object.  This includes weight, acoustic resonance, and (if conductive material is present) capacitive signature.

@@

\tovi{I would save these details for later, 
when we tlak about our actual 
implementations.}

### 2014-03-20 paper/exampleobjects.tex
integrate new temp figure
addressing some comments, but mostly just copying the tovi comments in

@@

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/radio.jpg}
\caption{This radio is assembled from traditional electronic components connected by copper-filled tubes.  The case was designed to allow the components to recess into it slightly.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:radio}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/sign.jpg}
\caption{A two-state animated neon sign designed using our tool (a)(b) \valkyrie{Tovi: we could use your PDF hax to make this animate in place :)}.  (c) shows the SVG input files to create this sign, and (d) shows an isometric view of the tubes created by our tool. \valkyrie{d) is a lot less interesting if we are making planar tubes.  also, for c, should we show an overlay of the two states?  maybe in different colors?}}
\label{fig:neon}
\end{figure}

>>>>

\tovi{Maybe a materials section 
before this - to talk about the 
specific materilas we used, 
such as the copper paint 
specifications, el lighting, etc.

Need to highlight which aspect of the design space each example object relates to. 
}

@@

\tovi{go into a bit more detail about modelling , fabrication, and
assembly process, and apparatus details (especially the 
copper paint - unless discussed earlier in a materials 
seciton.}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/radio.png}
\caption{This radio is assembled from traditional electronic components connected by copper-filled tubes.  The case was designed to allow the components to recess into it slightly.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:radio}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/sign.png}
\caption{A two-state animated neon sign designed using our tool (a)(b) \valkyrie{Tovi: we could use your PDF hax to make this animate in place :)}.  (c) shows the SVG input files to create this sign, and (d) shows an isometric view of the tubes created by our tool. \valkyrie{d) is a lot less interesting if we are making planar tubes.  also, for c, should we show an overlay of the two states?  maybe in different colors?}}
\label{fig:neon}
\end{figure}

### 2014-03-20 paper/introduction.tex
addressing some comments, but mostly just copying the tovi comments in

The generation of these pipes, however, is not trivial.  Pipes need to be as straight as possible to ease the insertion of media post-print.  Independent pipes should not intersect, as this could lead to electrical shorting or other problems.  Pipes should not pass too close to the surface (unless they are being used for display purposes).  Consumer-grade 3D printers do not guarantee air- or water-tightness of their prints, so more than one layer may be required to prevent leakage.  Finally, pipes

@@

\begin{itemize}
\item We lay out a design space of pipe-mediated interactive possibilities. 
\item We offer algorithms and techniques for routing pipes, as well as a design tool implementing them.
\item We showcase a set of examples, enabled by our modeling tool and exploring new points in the design space.
\end{itemize}
\bjoern{I'd say more about the software contribution in the abstract. Maybe that just requires expanding these bullets into a full paragraph.}

>>>>

The generation of these pipes, however, is not trivial.  Pipes need to be as straight as possible to ease the insertion of media post-print.  Independent pipes should not intersect, as this could lead to electrical shorting or other problems.  Pipes should not pass too close to the surface (unless they are being used for display purposes).  Consumer-grade 3D printers do not guarantee air- or water-tightness of their prints, so more than one layer may be required to prevent fluid leakage.  We have developed techniques for minimizing the bending energy of, enforcing non-intersection with, and avoiding the surface for pipes.  These techniques are embodied in our software tool to enable makers to create pipe-powered interfaces.

@@

\begin{itemize}
\item We lay out a design space of pipes and their types, contained media, topologies, and design focus.
\item We describe the interaction possibilities of pipes, including prior work as well as uncharted possibilities.
\item We offer algorithms and techniques for routing pipes, as well as a design tool implementing them.
\item We showcase a set of examples, enabled by our modeling tool and exploring new points in the design space.
\end{itemize}

### 2014-03-20 paper/relatedwork.tex
addressing some comments, but mostly just copying the tovi comments in

While using a series of tubes can replicate the interaction techniques discussed (and more), our work's \emph{contribution} is more generally related to two existing research areas: fabrication and routing.

\subsection{Fabrication}

Previous work has investigated the integration of interactivity into the fabrication process.  \cite{Willis-printedoptics} used light pipes, solid clear tubes, to create integrated displays: our work allows a superset of these capabilities, and Printed Optics is a part of our design space.  Willis, et al., also did not offer a design tool or techniques for creating light pipes automatically.  \cite{Savage-sauron} investigated the use of computer vision to track interactions with physical mechanisms.  Using tubes for redirection, it is possible to replicate these mechanically sensitive techniques (see Figure \ref{fig:pens}), however our work does not focus on computer vision alone.  Slyper, et al., \cite{Slyper-pressure} 3D printed flexible robot armatures capable of sensing interaction via changes in air pressure.  This technique is complementary to ours, as we allow for placing these interactive elements anywhere on an object's surface while they had to place them in locations accessible for electronics insertion.

@@

\subsection{Routing}

@@

>>>>

While using a series of tubes can replicate a variety of interaction techniques, our work's \emph{contribution} is more generally related to two existing research areas: fabrication and routing.

\subsection{Fabrication of Interactive Devices}

Previous work has investigated the integration of interactivity with the fabrication process.  \cite{Willis-printedoptics} used light pipes, solid clear tubes, to create integrated displays: our work allows a superset of these capabilities, and Printed Optics is a part of our design space.  Willis, et al., also did not offer a design tool or techniques for creating light pipes automatically.  \cite{Savage-sauron} investigated the use of computer vision to track interactions with physical mechanisms.  Using tubes for redirection, it is possible to replicate these mechanically sensitive techniques (see Figure \ref{fig:pens}), however our work does not focus on computer vision alone.  Slyper, et al., \cite{Slyper-pressure} 3D printed flexible robot armatures capable of sensing interaction via changes in air pressure.  This technique is complementary to ours, as we allow for placing these interactive elements anywhere on an object's surface while they had to place them in locations accessible for electronics insertion.

\subsubsection{Fabricating Channels}

@@

\subsection{Routing and Internal Modeling}

@@

Prior work on modeling the interior of objects (as opposed to their exterior) has been limited.  \valkyrie{ryan, can you give citations here?}  Sauron automatically modified the interior of existing mechanical objects to make them amenable to vision-based sensing \cite{Savage-sauron}, while Willis, et al.,'s Infrastructs project created encoded interior cavities in 3D printed objects designed to be sensed with a terahertz imaging tool.  Our work differs in that we want to allow users to design pipes and integrate interactive objects with them.

### 2014-03-20 paper/tubes.tex
addressing some comments, but mostly just copying the tovi comments in

@@

@@

>>>>

\tovi{discussion points 
- remove support material
-evenutally medium could be printed into tube}

@@

\tovi{Is this useful for anything other 
than the neon sign usage 
scenario? It's probably too 
detailed for the purpose which it 
serves}

@@

\tovi{I think this seciton is actually 
important. Should talk about 
support material, and 
feasability of printing hollow 
channels (vs channels with 
support material) on different 
printer models. 
Also talk about process of 
removing support material.
And finally, process of 
printing models in multiple 
pieces, to aid support material 
removal and threading.
Would be nice if the software 
automatically provided the 
slicing and snap together 
parts based on the channel 
geometry}
